PANCHANGE_analysis

### 2020-12-09 PANCHANGE_analysis.Rmd
created function for drawing forest plots in different congfigurations

lmoutput_format <- function(lmobject,explan_var,dfname){

@@

@@

  # Add category labels

  df$Categories <- categories

@@

  assign(dfname, df, envir = .GlobalEnv)

@@

>>>>

lmoutput_format <- function(lmobject,explan_var, group, dfname){

@@

  ## Disoprder dimension  
  groups <- c(group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group,
                  group)

@@

  # Add category labels
  df$Categories <- categories

  # Add group labels
  df$Group <- groups

@@

  # drop intercept row
    df <- df[(df$RowLabels != 'intercept'),]

  # order factors

  # assign dataframe to global environment
  assign(dfname, df, envir = .GlobalEnv)

@@

## Function to create forest plots

```{r function for creating forest plots}

lm.forest <- function(data,title)

  p = ggplot(data=data,
             aes(x =RowLabels,y = Estimate,
                colour = Group)) +

    geom_point(size = 2,
               position = position_dodge(0.9)) +

    geom_hline(aes(fill=Group),
               yintercept =0, 
               linetype=2)  +

    xlab('Group') + 
    ylab("Estimate (95% Confidence Interval)")  +
  ggtitle(title) +

    geom_errorbar(aes(ymin = LowerBound,
                      ymax = UpperBound),
                  width = .5,
                  position = position_dodge(0.9))  +

    facet_wrap(. ~ Categories,
               strip.position="left",nrow=5,scales = "free_y") +

  scale_colour_manual(values=COPINGpalette5) +

    theme(plot.title=element_text(size=20,face="bold"),
          axis.text.y=element_text(face="bold"),
          axis.text.x=element_text(face="bold"),
          axis.title.x=element_text(size=14,face="bold"),
          axis.title.y=element_blank(),
          strip.text.y = element_text(angle=180,face="bold"),
          panel.background = element_blank(),
          strip.background = element_rect(fill = "light grey"),
          panel.border = element_rect(colour = "grey",fill = NA)) +
    coord_flip()
  return(p)
